Meesters TODO List

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex
chapter 2 + 4

The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

@@

@@

Combining these solutions give solutions in the form the trial solutions:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions does indeed satisfy the differential equations with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

@@

\newtheorem{ThmVV06}{Theorem}
\begin{ThmVV06}
	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. Also all eigenvalues less than $\alpha$ are simple eigenvalues.
\end{ThmVV06}

>>>>

If such a $\lambda$ exists, it leads to the following problem called an eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

\textcolor{red}{Due to this periodicity of these solutions for} the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions. This solution is called the constant solution.

A systematic approach to get the eigenvalues and eigenfunctions is given in \cite{VV06}. This is discussed in in Section 4.2. The following theorem is derived from \cite{VV06} and confirms the validity of our trial solutions for the eigenvalue problem.

\newtheorem{ThmVV06}{Theorem}
\begin{ThmVV06}
	If $\langle u \ \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. Also all eigenvalues less than $\alpha$ are simple eigenvalues. The solution $\langle 0, 1 \rangle$ is a constant solution of Problem T-1E.
\end{ThmVV06}

\textcolor{red}{**************OLD VERSION******************}

@@

\newtheorem{ThmVV06_2}{Theorem}
\begin{ThmVV06_2}
	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. Also all eigenvalues less than $\alpha$ are simple eigenvalues.
\end{ThmVV06_2}

\textcolor{red}{********************************}

@@

Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions does indeed satisfy the differential equations with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

@@

### 2023-04-15 files/Chapter4/ModalAnalysisTimo.tex
chapter 2 + 4

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}

\section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
In section \ref{ssec:1D_Model:Modal} the idea of modal analysis is explored using a Timoshenko beam as an example. In this section, we look at the work of the authors of [VV06]. The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.\\

@@

\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.\\

\sout{For this section, the work of the authors of [VV06] is discussed. {Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.\\

@@

Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue. \\

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this section, more general theory for modal analysis of te Timoshenko beam theory is discuss, as well as some more examples of the application of the theory.
\section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
In section \ref{ssec:1D_Model:Modal} the idea of modal analysis is explored using a Timoshenko beam as an example. In this section, we look at the work of the authors of [VV06]. The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.

@@

\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.

\sout{For this section, the work of the authors of [VV06] is discussed. {Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.

@@

Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.
